### 2019-04-08 papers/journal/intro.tex
Intro Dia fixed

\noindent A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
%
These compartments exchange molecules amongst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
The molecular interaction network that controls the \unsure{Transport/Traffic}vesicle transport system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
Due to this, obtaining a complete understanding of the vesicle transport system through physical experimentation alone is a hard problem.
%
Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016wine, mani2016stacking}\change{Should only cite 3?}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
The phenomenology of vesicle traffic is unlikely to be familiar to many readers; however, the details are important for the rest of our discussion. 
%
Therefore, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
%
\subsection{Vesicle traffic system}
%Vesicles were discovered decades ago, in the early 1950s, and s
\noindent The major molecules involved in the vesicle traffic system~\cite{wells2005discovery} can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments. 
%
Below, we give a brief description of the sequence of steps involved in the vesicle transport process. 
%
Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.

@@

\subsubsection{Vesicle budding} \unsure{Somya should we say it involve three mojor steps? This line is not optimal. Use of "see" okay?}The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment, see Figure~\ref{fig:vts}.
%
\unsure{new line start or this is ok?}Cargo sorting is performed by cytosolic adaptor proteins. 
Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. 
%
Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%
Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
%

@@

\subsubsection{Vesicle fusion} \info{Calling them process okay?}The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle, Figure~\ref{fig:vts}.

@@

\subsection{The model}
\noindent \info{Ashutosh. Should we say this. We have done this uniformally.}The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
%
On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
%
The following are the basic component and assumptions of our model. 
\begin{enumerate}
\item A cell is a set of compartments exchanging vesicles.
\item Compartments are neither created nor destroyed~\cite{braell1984glycoprotein}.
\item Each compartment is in steady state, gain and loss of the molecules is balance~\cite{braell1984glycoprotein}.
\item Molecules are neither created nor destroyed~\cite{he2009differential}.
\item Molecules move via vesicles of uniform size.
\item Identical vesicles have identical target compartments~\cite{fries1981transient}.
\item Fusion of vesicles to compartments is driven by specific SNARE pairing~\cite{mcnew2000compartmental}.
%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle~\cite{mima2008reconstituted}.
\item An active SNARE pair is necessary and sufficient for fusion~\cite{weber1998snarepins}
. 
\end{enumerate}
%
All our assumptions, except assumption 5, are held up by cell biological results.
%
Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence for the \unsure{Is it a simplification or simplification to suite our Boolean Model. Should we say Boolean model? Or this looks fine?}sake of simplicity, we assume a uniform size for intracellular vesicles.
%The assumptions 
%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.

@@

\subsubsection{Vesicle fusion}
%Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
%
%Particularly, molecules composition (SNARE proteins etc) present on the budded vesicle determines it's properties, which 
% 
%The molecular composition and hence the properties of the transfer vesicle 
%is the crucial factor to which target compartment the vesicle will fuse to.
%
%For any given pair of a vesicle and a compartment, the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
%  
%Biophysically, fusion of a vesicle to the target compartment requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment.
%
%Once a vesicle has budded out of the source, the molecules it carries determine its properties. In particular, for any given pair of a vesicle and a compartment, the set of SNARE proteins that label the former and latter influence whether the vesicle will fuse to that compartment. Biophysically, fusion requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment. 
%
%SNAREs are of two types (known as Q and R in the cell biology iterature) and 
Vesicle fusion requires a pairing of 3 Q-SNAREs and 1 R-SNARE that are distributed between the transfer vesicle and the target compartment. 
%For any given pair of a vesicle and a compartment, vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE on 
%the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
%
%The list of molecular pairs that can drive a fusion event is given in a pairing matrix between Q and R SNAREs. 
%
Not all sets of \unsure{R-SNARE? or R SNARE is Okay?}Q and R SNAREs are allowed to fuse with each other.
%
%In the model, we assume that the cell has an equal number of Q and R SNARE types.
%
Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with Q and R SNAREs. 
% equal number of Q and R SNAREs as a part of node and edge label.
%
%
Given a relation of all allowed fusion SNARE pairings, we can computationally determine whether a particular transfer vesicle will fuse to a particular target compartment (the edge between two compartments) based on the above condition.

@@

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is \unsure{shld we say something about example in one line before the start?}complete.\\
%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\vspace{-0.5cm}
\begin{example}
%
In Figure~\ref{fig:M1}, \improve{require improvement in the description of this example}we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a string of molecule, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
%
\input{pm-1-matrix}
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%
\subsection{Combinatorial problem and use of Formal methods}
\noindent The analysis of vesicle traffic systems is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
%For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
%
%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool.
If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered by the same reason.

@@

\subsubsection{Size of the VTS system}
Let us discuss rough sizes of the system and expected behaviors.
%%
%A typical VTS may have about 10 compartments.
%%
%%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
%%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
%%
%The VTS may transport a large number of molecules but the molecules that
%are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
%%
%According to the definition the activity of molecules can be controlled by
%the presence of all other molecules.
%%
%However, in practice the activity of a molecule is controlled by
%the presence of ~2-3 other molecules.
A typical eukaryotic cell contains 9 organelles; the ER, the cis-, medial- and trans-Golgi, the early, late and recycling endosomes, the lysosome and the plasma membrane~\cite{lodish2008molecular}. 
%
The organellar content of cells vary across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhopteries and micronemes~\cite{gubbels2012evolution}. 
%
The organellar content may also vary across different states of the same cell, for e.g., during cell division, the Golgi apparatus disintegrates into vesicles~\cite{tang2013cell}. 
%
Also, across different cell-types, these organelles may be more or less differentiated, for example, number of stacks in the Golgi vary across different cells~\cite{polishchuk2004structural}. 
%

Going by the above description, we can assume that the VTS has of the order of 10 compartments. 
%
The VTS transports a large number of molecules but the molecules that actively control the system are in their tens [MBOC]. 
%
By definition the activity of any VTS molecules can be controlled by all other molecules.
%
However, in practice the activity of a molecule is directly controlled by 2-3 other molecules; for example, adaptor proteins are recruited to compartments by lipids of the compartment membrane and by ARF/SAR GTPases~\cite{kahn2009toward}. 
%
Some molecules, such as Rab GTPases are master regulators which control many different VTS molecules with diverse functions~\cite{zerial2001rab}. 
%
But most VTS molecules have more localized influence.
%
We use the above information during the encoding of all search problems presented later.

% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
%
%
% Note that the formulas define among other things constraints over
% paths between nodes in the graph model of VTS. Similarly, one can
% define fusion rules as constraints over the boolean functions modeling
% the regulations.  
% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
%\begin{itemize}
%\item \srivas{Detailed BIO to Graph problem}
%\end{itemize}
%Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e. the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.  Here we have defined the property by checking over existence of any fusion/budding rules.  We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
%
%\subsection{Converting the Graph Problem into Boolean SAT problem}
%\label{subsec:satproblem}
%To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.  In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.  We then used the CBMC model checker to convert the graph problem into a SAT problem.  One of the challenges we had in our earlier work is dealing with quantifiers.  Note that the connectedness property defined in Listing~1.2 has quantifier alternation.  Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.   CBMC supports only a quantifier-free logic n its assertion language.  In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.  This enumeration was one source of bottleneck for scaling in our earlier work.  In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.  The details of te hnew encding will described in subsequent sections.
%A VTS is {\em $k$-connected} if every pair of compartments remain reachable after dropping $k-1$ vesicles.
%
%This property of VTSs has been considered informative and studied by~\cite{shukla}.
%
%Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
\subsection{Synthesis of VTS }
\noindent The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}. 
%
Completing the vesicle traffic network is a difficult task for the many important reasons: 
\begin{enumerate}
	\item The core vesicle transport network is conserved across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different ~\cite{stoops2014trafficking,zhou2015arp2}.

@@

	\item Molecules can have redundant routes within the cell ~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
	\item Behaviour of traffic molecules in vitro is different from their behaviour inside cells ~\cite{furukawa2014multiple}.

	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
\end{enumerate}

Nonetheless, completing the vesicle traffic network for different organisms is very useful. 
%
Many diseases are caused by the malfunction of the vesicle traffic network. 
%
Knowledge of the complete network would be helpful in identifying the root causes~\cite{bexiga2013human,gissen2007cargos}. 
%
At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network, and would also allow us to decipher features such as parts of the traffic system that are unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our stability and k-connectivity constraints as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%
\begin{example}
	%
	In figure~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Figure~\ref{fig:synth-vts2} present it's complete output VTS. 
	%
	The synthesis is performed against the steady state property and 3-connectivity. The tags PM, EE, and LE represent the corresponding nodes (please refer to Appendix~\ref{sec:ex-vts} for proper discussion about the nodes and molecules depicted in the diagram). 
	%
	Synthesized edge is in red color and synthesized molecules are represented with blue.
	%
	The synthesis added one edge and 7 molecules to complete the partial VTS.
	%
	For clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.

>>>>

\noindent A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
%
These compartments exchange molecules amongst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
The molecular interaction network that controls the \unsure{Transport/Traffic}vesicle transport system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
Due to this, obtaining a complete understanding of the vesicle transport system through physical experimentation alone is a hard problem.
%
Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
The phenomenology of vesicle traffic is unlikely to be familiar to many readers; however, the details are important for the rest of our discussion. 
%
Therefore, we give an overview of the molecular mechanism of the VTS and then we sketch out a few interesting problems that are key to an understanding of the VTS.
%
\subsection{Vesicle traffic system}
%Vesicles were discovered decades ago, in the early 1950s, and s
\noindent The major molecules involved in the vesicle traffic system~\cite{wells2005discovery} can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments. 
%
Below, we give a brief description of the sequence of steps involved in the vesicle transport process. 
%
Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.

@@

\subsubsection{Vesicle budding} \unsure{Somya should we say it involve three mojor steps? This line is not optimal.}The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Figure~\ref{fig:vts}).
%
Cargo sorting is performed by cytosolic adaptor proteins. 
Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. 
%
Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%
Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
%

@@

\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle, Figure~\ref{fig:vts}.

@@

\subsection{The model}
\noindent The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
%
On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
%
The following are the basic component and assumptions of our model. 
\begin{enumerate}
\item A cell is a set of compartments exchanging vesicles.
\item Compartments are neither created nor destroyed~\cite{braell1984glycoprotein}.
\item Each compartment is in steady state, gain and loss of the molecules is balance~\cite{braell1984glycoprotein}.
\item Molecules are neither created nor destroyed~\cite{he2009differential}.
\item Molecules move via vesicles of uniform size.
\item Identical vesicles have identical target compartments~\cite{fries1981transient}.
\item Fusion of vesicles to compartments is driven by specific SNARE pairing~\cite{mcnew2000compartmental}.
%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle~\cite{mima2008reconstituted}.
\item An active SNARE pair is necessary and sufficient for fusion~\cite{weber1998snarepins}
. 
\end{enumerate}
%
All our assumptions, except assumption 5, are held up by cell biological results.
%
Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence for the sake of simplicity, we assume a uniform size for intracellular vesicles.
%The assumptions 
%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.

@@

\subsubsection{Vesicle fusion}
%Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
%
%Particularly, molecules composition (SNARE proteins etc) present on the budded vesicle determines it's properties, which 
% 
%The molecular composition and hence the properties of the transfer vesicle 
%is the crucial factor to which target compartment the vesicle will fuse to.
%
%For any given pair of a vesicle and a compartment, the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
%  
%Biophysically, fusion of a vesicle to the target compartment requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment.
%
%Once a vesicle has budded out of the source, the molecules it carries determine its properties. In particular, for any given pair of a vesicle and a compartment, the set of SNARE proteins that label the former and latter influence whether the vesicle will fuse to that compartment. Biophysically, fusion requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment. 
%
%SNAREs are of two types (known as Q and R in the cell biology iterature) and 
Vesicle fusion requires a pairing of 3 Q-SNAREs and 1 R-SNARE that are distributed between the transfer vesicle and the target compartment. 
%For any given pair of a vesicle and a compartment, vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE on 
%the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
%
%The list of molecular pairs that can drive a fusion event is given in a pairing matrix between Q and R SNAREs. 
%
Not all sets of Q and R-SNAREs are allowed to fuse with each other.
%
%In the model, we assume that the cell has an equal number of Q and R SNARE types.
%
Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with Q and R-SNAREs. 
% equal number of Q and R SNAREs as a part of node and edge label.
%
%
Given a relation of all allowed fusion SNARE pairings, we can computationally determine whether a particular transfer vesicle will fuse to a particular target compartment (the edge between two compartments) based on the above condition.

@@

%\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
%\somya{But this is the para where we explain why connectivity is interesting an biological property}
%\ankit{Yes; Both of our remark looks correct!}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.\\
%
%\begin{table}[!t]
%	\caption{Table Caption}
%	\label{tab1}
%	\centering
%	{\setlength\tabcolsep{0.1pt}%
%		\begin{tabular}{ccccccccccccccc}
%			& $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ && & $D_1$ & $D_2$ & $D_3$ & $D_4$ & $D_5$ & $D_6$ \\
%			$D_1$ & & \cca{0} & \cca{0} & \cca{0} & \cca{2} & \cca{0} && $D_1$ && \cca{0} & \cca{0} & \cca{2} & \cca{2} & \cca{2} \\
%			$D_2$ & \cca{0} & & \cca{2} & \cca{0} & \cca{2} & \cca{0} && $D_2$ & \cca{0} &  & \cca{3} & \cca{0} & \cca{0} & \cca{2} \\
%			$D_3$ & \cca{7} & \cca{4} &  & \cca{3} & \cca{0} & \cca{4} && $D_3$ & \cca{0} & \cca{4} &  & \cca{4} & \cca{2} & \cca{0} \\
%			$D_4$ & \cca{3} & \cca{0} & \cca{7} &  & \cca{4} & \cca{0} && $D_4$ & \cca{0} & \cca{0} & \cca{5} &  & \cca{0} & \cca{0} \\
%			$D_5$ & \cca{3} & \cca{7} & \cca{7} & \cca{2} &  & \cca{4} && $D_5$ & \cca{2} & \cca{2} & \cca{0} & \cca{4} &  & \cca{4} \\
%			$D_6$ & \cca{2} & \cca{2} & \cca{7} & \cca{2} & \cca{6} &  && $D_6$ & \cca{2} & \cca{2} & \cca{3} & \cca{0} & \cca{4} & \\
%	\end{tabular}}
%\end{table}
%
\vspace{-0.5cm}
\begin{example}
%
In Figure~\ref{fig:M1}, we present a VTS that has 2 compartments and 18 molecules with its corresponding pairing matrix.
%
%Molecules are represented as $Q_{i}$'s or $R_{i}$'s to make a clear distinction between Q and R SNAREs.
%
In the VTS, labels are a string of molecule, where we show active molecules in red color.
%
The activity of the molecules on the node is controlled
by the presence of the other molecules (exact Boolean function is not shown). 
%
The activity of the molecules on an edge is determined by the corresponding pairing matrix.
%
Note that molecules $X$ and $Y$ do not take part in the fusion but play a part in determining activity at the corresponding nodes.
%
Below the VTS, we show the pairing matrix.
%
Rows in the matrix correspond to the labels of edges, and columns correspond to the labels of nodes.
%
An entry 1 represents pairing between molecules and 0 represents no pairing.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 4-connected graph.
\end{example}
%
\input{pm-1-matrix}
%\subsection{Modeling and Symbolic Analysis of VTS: An Overview}
\label{subsec:graphmodel}
%
\subsection{Combinatorial problem and use of Formal methods}
\noindent The analysis of vesicle traffic systems is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
%For example, we might want to check some conjecture of interest for all graphs of a certain structure. 
%
%If the analysis is done on a large number of graphs, the joined effect of large quantity of graphs and combinatorially many possible regulatory rules will be difficult to handle by any tool.
If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered by the same reason.

@@

\subsubsection{Size of the VTS system}
Let us discuss the rough sizes of the system and expected behaviors.
%%
%A typical VTS may have about 10 compartments.
%%
%%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
%%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
%%
%The VTS may transport a large number of molecules but the molecules that
%are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
%%
%According to the definition the activity of molecules can be controlled by
%the presence of all other molecules.
%%
%However, in practice the activity of a molecule is controlled by
%the presence of ~2-3 other molecules.
A typical eukaryotic cell contains 9 organelles; the ER, the cis-, medial- and trans-Golgi, the early, late and recycling endosomes, the lysosome and the plasma membrane~\cite{lodish2008molecular}. 
%
The organellar content of cells varies across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhoptries and micronemes~\cite{gubbels2012evolution}. 
%
The organellar content may also vary across different states of the same cell, for e.g., during cell division, the Golgi apparatus disintegrates into vesicles~\cite{tang2013cell}. 
%
Also, across different cell-types, these organelles may be more or less differentiated, for example, the number of stacks in the Golgi varies across different cells~\cite{polishchuk2004structural}. 
%

Going by the above description, we can assume that the VTS has of the order of 10 compartments. 
%
The VTS transports a large number of molecules but the molecules that actively control the system are in their tens~\cite{lodish2008molecular}. 
%
By definition, the activity of any VTS molecules can be controlled by all other molecules.
%
However, in practice the activity of a molecule is directly controlled by 2-3 other molecules; for example, adaptor proteins are recruited to compartments by lipids of the compartment membrane and by ARF/SAR GTPases~\cite{kahn2009toward}. 
%
Some molecules, such as Rab GTPases are master regulators which control many different VTS molecules with diverse functions~\cite{zerial2001rab}. 
%
But most VTS molecules have more localized influence.
%
We use the above information during the encoding of all search problems presented later.

% i.e., formally as a boolean function that given requisite labels of nodes and vesicles that returns true if the required regulations are met. 
%
%
% Note that the formulas define among other things constraints over
% paths between nodes in the graph model of VTS. Similarly, one can
% define fusion rules as constraints over the boolean functions modeling
% the regulations.  
% For example, the steady state condition, described informally earlier, can be defined by the formula shown in Listing~1.1.
%\begin{itemize}
%\item \srivas{Detailed BIO to Graph problem}
%\end{itemize}
%Given definitions of fusion and budding rules and the steady state conditions, whether a VTS meets maximum connectivity requirement, i.e. the LGC property, can be verified by checking if the formula show in Listing~1.2 is valid.  Here we have defined the property by checking over existence of any fusion/budding rules.  We can eliminate the existential quantifier if we are interested in checking the property for a particular fusion/budding rule.
%
%\subsection{Converting the Graph Problem into Boolean SAT problem}
%\label{subsec:satproblem}
%To convert the graph problem described in sec~\ref{subsec:graphmodeling}, into a boolean SAT problem, we need to define a scheme to represent graphs and boolean functions using a suitable set of propositional variables.  In our earlier work, we modeled the graph problem in C using arrays to model graphs and boolean function.  We then used the CBMC model checker to convert the graph problem into a SAT problem.  One of the challenges we had in our earlier work is dealing with quantifiers.  Note that the connectedness property defined in Listing~1.2 has quantifier alternation.  Even if we were to eliminate the existential quantifier by instantiating the problem for a fixed set of fusion rules, we would have embedded quantifiers in the antecedent of implications.   CBMC supports only a quantifier-free logic n its assertion language.  In our earlier work we used a combination of explicit enumeration at the C-level and clever use f non-determinism to eliminate alternation of quantifiers.  This enumeration was one source of bottleneck for scaling in our earlier work.  In the current work we eliminate this bottleneck by modeling the problem directly as a SAT instance using uninterpreted functions and recursive relations.  The details of te hnew encding will described in subsequent sections.
%A VTS is {\em $k$-connected} if every pair of compartments remain reachable after dropping $k-1$ vesicles.
%
%This property of VTSs has been considered informative and studied by~\cite{shukla}.
%
%Here we have build an {\em efficient} tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
\subsection{Synthesis of VTS }
\noindent The current picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and new vesicle routes are being discovered every year~\cite{nickel2018unconventional,weill2018toolbox}. 
%
Completing the vesicle traffic network is a difficult task for the many important reasons: 
\begin{enumerate}
    \item The core vesicle transport network is conserved across eukaryotes, the traffic network in different organisms~\cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.

@@

    \item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
    \item Behaviour of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}.

    \item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
\end{enumerate}

Nonetheless, completing the vesicle traffic network for different organisms is very useful. 
%
Many diseases are caused by the malfunction of the vesicle traffic network. 
%
Knowledge of the complete network would be helpful in identifying the root causes of ~\cite{bexiga2013human,gissen2007cargos}. 
%
At a more basic level, having complete pictures of the vesicle traffic system for various organisms and various cell-types would allow comparative studies, and therefore would allow the deduction of modes of evolution of the form of the traffic network. 
%
This would also allow us to decipher features such as parts of the traffic system that is unchanging, and therefore likely to be its core, and parts that are more plastic \cite{barlow2017seeing}.

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our stability and k-connectivity constraints as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%
\begin{example}
	%
    In figure~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Figure~\ref{fig:synth-vts2} present it's complete output VTS. 
    %
    The synthesis is performed against the steady state property and 3-connectivity. 
    %The tags PM, EE, and LE represent the corresponding nodes (please refer to Appendix~\ref{sec:ex-vts} for a proper discussion about the nodes and molecules depicted in the diagram). 
    %
    Synthesized edge is in red color and synthesized molecules are presented in blue.
    %
    The synthesis adds one edge and 7 molecules to complete the partial VTS.
    %
    For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
